Classless Java

### 2016-03-24 OOPSLA16/sections/FutureWork.tex
Some little changes to sect 6

This section discusses some possible future work, including native
language support for IB.

@@

A limitation of our approach, inherited from Java, is the lack of some
support for encapsulation: in Java interfaces all methods are public.
However, it is possible to workaround the
limitations of interfaces by a
 variation of the facade pattern~\cite{BettiniDSS13}:
\begin{lstlisting}
@Obj interface InternalData implements ExposedData {
    /*all the methods*/} //package visibility
public interface ExposedData {
  /*just the exposed interface*/
  static ExposedData of(...) {
    return InternalData.of(...);}  }
\end{lstlisting}

@@

We may also want to offer a compact syntax for property updaters and generalized with methods;
\begin{lstlisting}
obj interface Foo{
  updater Bar, Beer;//declares imperative updaters:
  //Foo set(Bar val); Foo set(Beer val);
  with Foo, Beer;//declared functional updaters:
  //Foo with(Bar val); Foo with(Beer val);
}
\end{lstlisting}
Finally, certain methods may have a specific meaning. For example
if a method called \Q@postInit@ is present, it will be called after construction.
It may be handled specially during multiple implementations, so that all relevant \Q@postInit@ methods are
called in some order.

>>>>

%This section discusses some possible future work, including native
%language support for IB.

@@

A limitation of our approach, inherited from Java, is the lack of some
support for encapsulation: in Java interfaces all methods are public.
However, it is possible to workaround the
limitations of interfaces by a
 variation of the facade pattern (as suggested by~\cite{BettiniDSS13}):
\begin{lstlisting}
@Obj interface InternalData implements ExposedData {
    /*all the methods*/} //package visibility
public interface ExposedData {
  /*just the exposed interface*/
  static ExposedData of(...) {
    return InternalData.of(...);}  }
\end{lstlisting}

@@

We may also want to offer a compact syntax for property updaters and generalized with methods;
\begin{lstlisting}[morekeywords={with}]
obj interface Foo{
  updater Bar, Beer;//declares imperative updaters:
  //Foo set(Bar val); Foo set(Beer val);
  with Foo, Beer;//declared functional updaters:
  //Foo with(Bar val); Foo with(Beer val);
}
\end{lstlisting}
Finally, certain methods may have a specific meaning. For example
if a method called \Q@postInit@ is present, it will be called after construction.
It may be handled specially during multiple implementations, so that all relevant \Q@postInit@ methods are
called in some order.
